
\begin{vitaesection}{Education}
\vspace{-0.1cm}
\item [2018]    Ph.D. in Electrical and Computer Engineering (Expected), University of California, Santa Barbara
\item [2007]    M.S. in Mechanical Engineering, Stanford University
\item [2006]    B.S. in Mechanical Engineering, University of California, Santa Barbara
\end{vitaesection}

\begin{vitaesection}{Experience}
\vspace{-0.1cm}
\item [2012 -- 2017] Graduate Student Researcher, University of California, Santa Barbara
\item [2008 -- 2012] Controls Engineer, AeroVironment
\item [2016] Instructor of Record, {\it COMP 150: Introduction to Object Oriented Programming}, California State University at Channel Islands
\item [2015] Certificate in College and University Teaching, UCSB
\item [2015] Mentor, Robotics internship, Institute for Collaborative Biotechnology, UCSB
\item [2015] Instructor of Record, {\it ENGR 3: Introduction to Programming}, UCSB
\item [2015] Mentor, School of Scientific Thought, Center for Science and Engineering Partnerships, UCSB
\item [2014] Teaching Assistant, {\it ENGR 3: Introduction to Programming}, UCSB
\item [2014] Teaching Assistant, {\it ECE 147C: Control System Design Project}, UCSB
\end{vitaesection}


\textbf{Publications}

\vspace{-0.1cm}


\vspace{0.1cm}

A. Alanwar, F. M. Anwar, Y. Zhang, J. Pearson, J. Hespanha, M. B. Srivastava. ``Cyclops: PRU Programming Framework for Precise Timing Applications.'' {\it Proc. of the 2017 IEEE International Symposium on Precision Clock Synchronization for Measurement, Control, and Communication (ISPCS)}, Aug. 2017. 

\vspace{0.1cm}

J. Pearson, J. Hespanha, D. Liberzon. ``Control with minimal cost-per-symbol encoding and quasi-optimality of event-based encoders.'' {\it IEEE Transactions on Automatic Control}, May 2017. 

\vspace{0.1cm}

J. Pearson, J. Hespanha, D. Liberzon. ``Quasi-optimality of event-based encoders.'' {\it Proc. of the 54th Conference on Decision and Control}, Dec. 2015.

\vspace{0.1cm}

J. Pearson, J. Hespanha, D. Liberzon. ``Control with Minimum Communication Cost per Symbol.'' {\it Proc. of the 53nd Conference on Decision and Control}, Dec. 2014.
